On the performance of the MAC model

### 2018-10-31 2018_nips_vigil/appendix.tex
table: colors/shapes combinations between CLEVR, CLEVR CoGenT-A and CLEVR CoGenT-B

\begin{enumerate}
\item Some description (with link to the paper) about the datasets. Maybe we can "import" material from main paper, making it lighter...
\item Table with attributes/feature combinations of CLEVR/CoGenT-A/CoGenT-B
\item Some exemplary pictures?
\end{enumerate}

>>>>

\begin{enumerate}
\item Some description (with link to the paper) about the datasets. Maybe we can "import" material from main paper, making it lighter...
\item Table with attributes/feature combinations of CLEVR/CoGenT-A/CoGenT-B

\begin{table}
	\centering
	\begin{tabular}{ccccCcCc}
		\toprule
		Dataset        & Cubes              & Cylinders &  Spheres         \\
		\midrule
		CLEVR   &  any color &  any color        &    any color    \\
		%\midrule
		CLEVR CoGenT A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
		CLEVR CoGenT B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
		\bottomrule
	\end{tabular}
	\caption{Comparison of the different colors/shapes combinations between CLEVR, CLEVR CoGenT-A and CLEVR CoGenT-B  }
	\label{tab:parameters}
\end{table}

\item Some exemplary pictures?
\end{enumerate}
